Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-12-10 batchdedup/eval.tex
added metrics section.

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Throughput (GB/s)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y=throughput] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average throughput for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Backup Time (min)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y expr=(\thisrow{avgbackuptime})/60] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average vm backup time for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Turnaround Time (min)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y expr=(\thisrow{turnaround})/60] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average vm turnaround time for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}

\todo{The names of the algorithms are just the temporary names I've been using for coding, DBP2 is the relative of the dual bin packing algorithm, BPL is the machine by machine largest VM to shortest round algorithm}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Total Jobspan (s)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                %legend pos=north west
		]
                \addplot table[x=Rounds,y=DBP2jobspan] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y=BPLjobspan] {figures/packing_comparison.txt};
                \legend{DBP2, BPL};
		\end{axis}
	\end{tikzpicture}
  \caption{Jobspan for DBP2 and BPL}
  \label{fig:jobspan-comparison}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Throughput (GB/s)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y=throughput] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average throughput for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Average Backup Time (min)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rounds,y expr=(\thisrow{avgbackuptime})/60] {figures/sim_full.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{simulated results for average vm backup time for individual VMs in 100 node cluster.}
  \label{fig:mpibuf-mem}
\end{figure}

%TODO: make this figure
%\begin{figure}[ht]
%  \centering
%	\begin{tikzpicture}
%		\begin{axis}[
%		%title={Network Buffer Size},
%		xlabel={Rounds},
%		ylabel={Backup Cost},
%		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
%		%legend pos=north west
%		]
%                \addplot table[x=rounds,y=DBP2Cost] {figures/cost.txt};
%                %\legend{Total Backup Time};
%		\end{axis}
%	\end{tikzpicture}
%  \caption{simulated results for backup cost based on real 120 node cluster.}
%  \label{fig:mpibuf-mem}
%\end{figure}

\todo{The names of the algorithms are just the temporary names I've been using for coding, DBP2 is the relative of the dual bin packing algorithm, BPL is the machine by machine largest VM to shortest round algorithm}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Total Jobspan (m)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                %legend pos=north west
		]
                \addplot table[x=Rounds,y expr=(\thisrow{DBP2jobspan})/60] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{BPLjobspan})/60] {figures/packing_comparison.txt};
                \legend{DBP2, BPL};
		\end{axis}
	\end{tikzpicture}
  \caption{Jobspan for DBP2 and BPL}
  \label{fig:jobspan-comparison}
\end{figure}
